Multifunctional Lipid Probes Primer

### 2025-01-21 TrifunctionalLipidProbesOverview.qmd
Minor formatting changes, overview structure added

---
title: "Trifunctional Lipid Probes Primer"
author: "Gaelen Guzman"
format: 
  html:
    embed-resources: false
standalone: true
---

@@

>>>>

---
title: "Multifunctional Lipid Probes Primer"
author: "Gaelen Guzman"
format: 
  html:
    embed-resources: false
standalone: true
---

@@

## Functional moieties

:::{.border}
![](/LipidProbe/Structures/SphingosineStructure.png){group="ProbePrimer"}
:::

### Terminal Alkyne

### Diazirine: A photo-activated crosslinker

### Coumarin Cage: A photo-activated protection moiety

## *P*hoto*a*ctivatable & *C*lickable Probes

## Trifunctional Lipid Probes

## Experimental schema

### Cell treatment

### Protein collection

### Mass spectrometry analysis

#### Spectral counting

#### Isobaric mass tagging
